Supporting Information for "Imperfect slope measurements drive overestimation in geometric models of lake depth"

### 2021-02-15 manuscript/si_template_2019.tex
report that categories are quantile bins

\begin{figure}
      \begin{center}
        \includegraphics[width=0.79\textwidth,keepaspectratio]{../figures/slope_by_area_depth-1}
      \end{center}
      \caption{Comparison between in-lake and nearshore slopes in concave and convex lakes of the same size and max depth.}\label{figS5}
    \end{figure}
\clearpage

>>>>

\begin{figure}
      \begin{center}
        \includegraphics[width=0.79\textwidth,keepaspectratio]{../figures/slope_by_area_depth-1}
      \end{center}
      \caption{Comparison between in-lake and nearshore slopes in concave and convex lakes of the same size and max depth. Categories are quantile bins ($<$ 25\%, 25-50\%, 50-75\%, and 75-100\%).}\label{figS5}
    \end{figure}
\clearpage
